---
title: "Use Cases"
author: "Daniel Chen"
date: "4/15/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data(iris)
source('resample.R')
source('cross_validate.R')
source('Funnels.R')
hv = hypervolume(iris[,c(1, 2)])
```

## Generate Hypervolume and Resample
Using the hypervolume that models the first two columns of the iris data set, we generate a sequence of bootstraps.
```{r}
# Samples i rows from the data that generated hv for each i in seq, then generates a bootstrap on each of these i resamples and saves to file.
# Runtime ~2hrs
# hv_bootstrap_seq <- resample('hv_bootstrap_seq', hv, method = 'bootstrap seq', points_per_resample = "sample size", seq = seq(10, 150, length.out = 29))
# Here is the result of running the above code
hv_bootstrap_seq <- "./Objects/hv_bootstrap_seq"
```

By creating funnel plots using the bootstrap sequence, we can see that our mean resampled data and mean random points both converge to the mean of our original sample.
```{r, fig.show='hold', out.width='50%'}
funnel(hv_bootstrap_seq, title = 'From resampled data', func = function(x) {mean(x@Data[,1])}) + 
  geom_line(aes(y = mean(hv@Data[,1]))) + 
  ylim(5.25, 6.5) +
  ylab('Mean Sepal Length')
funnel(hv_bootstrap_seq, title = 'From random points', func = function(x) {mean(x@RandomPoints[,1])}) + 
  geom_line(aes(y = mean(hv@Data[,1]))) + 
  ylim(5.25, 6.5) +
  ylab(NULL)
```

Variance of a kernel density estimate is greater than sample variance as expected, but converges to sample variance for large n.  
Bootstrapped volumes seem unbiased; however the 95% confidence interval is skewed.
```{r, fig.show='hold', out.width='50%'}
funnel(hv_bootstrap_seq, title = 'Resampled variances from random points', func = function(x) {var(x@RandomPoints[,1])}) + 
  geom_line(aes(y = var(hv@Data[,1])))

funnel(hv_bootstrap_seq, title = 'Resampled volumes', func = get_volume) + 
  geom_line(aes(y = get_volume(hv)))
```

## Biased resample
We consider the iris dataset and want to see how a biased sampling method affects the data.
For example, we suspect flowers with larger and more visible petals are over counted.
To simulate overcounting petals, we perform a biased bootstrap.
```{r}
# Hypervolume generated from iris data
hv = hypervolume(iris[,1:4])
# Weigh points with large values for petal length and petal width higher
biased_path = resample("Petal bias", hv, method = "biased bootstrap", n = 1, mu = apply(hv@Data, 2, max)[c("Petal.Length", "Petal.Width")], sigma = apply(hv@Data, 2, sd)[c("Petal.Length", "Petal.Width")]*2, cols_to_bias = c("Petal.Length", "Petal.Width"))
biased_hv = readRDS(file.path(biased_path, "resample 1.rds"))
```
```{r, fig.show='hold', out.width='50%'}
ggplot(data.frame(hv@Data), aes(y = ..density..)) + 
  geom_histogram(aes(x = Petal.Width), bins = 20, fill = 'blue', alpha = 0.5) + 
  geom_histogram(aes(x = Petal.Length), bins = 20, fill = 'red', alpha = 0.5) + 
  ggtitle("Unbiased distribution of petal length and width")
ggplot(data.frame(biased_hv@Data), aes(y = ..density..)) + 
  geom_histogram(aes(x = Petal.Width), bins = 20, fill = 'blue', alpha = 0.5) + 
  geom_histogram(aes(x = Petal.Length), bins = 20, fill = 'red', alpha = 0.5) + 
  ggtitle("Biased distribution of petal length and width")
```
Effect on sepal width and sepal length
```{r, fig.show='hold', out.width='50%'}
ggplot(data.frame(hv@Data), aes(y = ..density..)) + 
  geom_histogram(aes(x = Sepal.Width), bins = 20, fill = 'blue', alpha = 0.5) + 
  geom_histogram(aes(x = Sepal.Length), bins = 20, fill = 'red', alpha = 0.5) + 
  ggtitle("Unbiased distribution of sepal length and width")
ggplot(data.frame(biased_hv@Data), aes(y = ..density..)) + 
  geom_histogram(aes(x = Sepal.Width), bins = 20, fill = 'blue', alpha = 0.5) + 
  geom_histogram(aes(x = Sepal.Length), bins = 20, fill = 'red', alpha = 0.5) + 
  ggtitle("Biased distribution of sepal length and width")
```
